### 2021-02-23 evaluation.tex
Revert "Shave off content by commenting out to reduce page count to 15"
This reverts commit 8bcb7bd7cfc6eae12b44593c1d66122cb987f2a6.

%In the process of training,
%we tracked three metrics on the training and validation sets:
%loss, accuracy, and solver performance on a sample of 1000 problems.
%A typical training ran for approximately 500 epochs
%with training loss steadily decreasing and
%validation loss decreasing for the initial 50 epochs and then increasing.
%Both training and validation accuracy were steadily increasing (training accuracy significantly faster than validation accuracy),
%with validation loss entering a plateau around epoch 100.
%The solver performance approximately followed the dynamics of the accuracy on the respective problem set.
% Predicate: https://ui.neptune.ai/filipbartek/vampire-ml/e/VML-540/charts
% Function: https://ui.neptune.ai/filipbartek/vampire-ml/e/VML-672/charts

>>>>

In the process of training,
we tracked three metrics on the training and validation sets:
loss, accuracy, and solver performance on a sample of 1000 problems.
A typical training ran for approximately 500 epochs
with training loss steadily decreasing and
validation loss decreasing for the initial 50 epochs and then increasing.
Both training and validation accuracy were steadily increasing (training accuracy significantly faster than validation accuracy),
with validation loss entering a plateau around epoch 100.
The solver performance approximately followed the dynamics of the accuracy on the respective problem set.
% Predicate: https://ui.neptune.ai/filipbartek/vampire-ml/e/VML-540/charts
% Function: https://ui.neptune.ai/filipbartek/vampire-ml/e/VML-672/charts

### 2021-02-23 main.tex
Revert "Shave off content by commenting out to reduce page count to 15"
This reverts commit 8bcb7bd7cfc6eae12b44593c1d66122cb987f2a6.

%A more detailed analysis of the training process might yield insights into how the performance generalizes
%from the training set to the validation set
%and from proxy metrics, such as the loss and the accuracy, to the final solver performance.
%Ultimately, this might reveal modifications that make the training more efficient and the final recommender more performant.
%
%The training examples take the form of pairs of precedences,
%where one of the precedences is preferable over the other.
%In this work, the amount by which the quality of the precedences differs is ignored.
%Taking the exact or estimated numbers of saturation loop iterations into account
%might help the recommender to prioritize the more significant gains.
%
%Applying techniques of reinforcement learning to focus the training data on the cases that yield high performance gains
%could further improve the recommender performance.
%
%We restricted our experiments to problems whose graph representation does not exceed \num{100000} nodes.
%Evaluating the recommender on larger problems would be an interesting test of generalization.
%Training on larger problems may be facilitated by employing a lossy graphification.
%
%We performed all experiments with a fixed \gls{atp} \Vampire{} and a fixed configuration
%we consider to be a reasonable baseline.
%Introducing other prover configurations (namely other \glspl{sot})
%or other provers could make the resulting recommender more robust
%and possibly help extract more general knowledge about the structure of good symbol precedences.
%
%Finally, the approach outlined in \cref{sec:architecture}
%could be adjusted to solve tasks on \gls{fol} formulas other than recommending symbol precedences,
%such as premise selection of given clause selection.
%On the other hand, we could try to solve other tasks that involve generating permutations of arbitrary length.
%\todo{FB: TSP? Probably not because it is too combinatorial.}

>>>>

A more detailed analysis of the training process might yield insights into how the performance generalizes
from the training set to the validation set
and from proxy metrics, such as the loss and the accuracy, to the final solver performance.
Ultimately, this might reveal modifications that make the training more efficient and the final recommender more performant.

The training examples take the form of pairs of precedences,
where one of the precedences is preferable over the other.
In this work, the amount by which the quality of the precedences differs is ignored.
Taking the exact or estimated numbers of saturation loop iterations into account
might help the recommender to prioritize the more significant gains.

Applying techniques of reinforcement learning to focus the training data on the cases that yield high performance gains
could further improve the recommender performance.

We restricted our experiments to problems whose graph representation does not exceed \num{100000} nodes.
Evaluating the recommender on larger problems would be an interesting test of generalization.
Training on larger problems may be facilitated by employing a lossy graphification.

We performed all experiments with a fixed \gls{atp} \Vampire{} and a fixed configuration
we consider to be a reasonable baseline.
Introducing other prover configurations (namely other \glspl{sot})
or other provers could make the resulting recommender more robust
and possibly help extract more general knowledge about the structure of good symbol precedences.

Finally, the approach outlined in \cref{sec:architecture}
could be adjusted to solve tasks on \gls{fol} formulas other than recommending symbol precedences,
such as premise selection of given clause selection.
On the other hand, we could try to solve other tasks that involve generating permutations of arbitrary length.
\todo{FB: TSP? Probably not because it is too combinatorial.}

%KBO is a also parametrized by weights (along with the precedence). Could we learn those as well? (Jointly?)
